Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-06-20 paper/paper.tex
a small pass on the abstract

The present paper proposes a \textit{process model}
that tries to explain \textit{how}
the DMN may implement
continuous evaluation and prediction of the environment to guide behavior.
%
DMN function is recast in mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
%
We argue that our formal account of DMN function naturally accommodates as special cases
the previously proposed cognitive accounts on
(1) predictive coding,
(2) semantic associations, and
(3) a ``sentinel'' role.
%
Moreover, this process model for the neural optimization of complex behavior in the DMN
offers parsimonious explanations for
recent experimental findings in animals and humans.
\end{abstract}

>>>>

In the present manuscript, we propose a \textit{process model}
that attempts to explain \textit{how} the DMN may implement
continuous evaluation and prediction of the environment to guide behavior.
%
We first review the rich literature on the DMN and recognize that the DMN contains the sufficient neuro-biological substrates to implement a full-blown reinforcement-learning agent, at least in principle. DMN function is then recast in mathematical terms of
control theory and reinforcement learning based on Markov decision processes.
%
We argue that our formal account of DMN function naturally accommodates as special cases
the previously proposed cognitive accounts on
(1) predictive coding,
(2) semantic associations, and
(3) a ``sentinel'' role.
%
Moreover, this process model for the neural optimization of complex behavior in the DMN
offers parsimonious explanations for
recent experimental findings in animals and humans.
\end{abstract}
